Analyzing Coopetition Strategies of Services within Communities

### 2012-11-24 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Added matlab file

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts web services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a random reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the web service cannot
compete, the procedure would suggest to collaborate, which is
better than competing and failing to obtain the task. In this case
(i.e., competing and not getting the task), the service stays idle
but still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some web services to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to get a task. This kind of
strategy selection is totally stochastic while the task allocation
algorithm follows a logical path. The ideal system is the one that
analyzes the optimal strategic path and consistently follows
strategies that bring maximum outcome. The result regarding the
community that follows the random strategy shows how stochastic
decision making degrades the community budget, but still this
result outperforms the one of the purely competitive community. In
the last case, all the services follow the competitive strategy
and the frequency of getting rejected from a task is relatively
high. In a community with limited number of tasks, the competitive
strategy for all services highly influences the community budget
because a potential group of services are losing at every run.

@@

>>>>

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts web services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a random reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the web service cannot
compete, the procedure would suggest to collaborate, which is
better than competing and failing to obtain the task. In this case
(i.e., competing and not getting the task), the service stays idle
but still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some web services to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to perform a task with high QoS requirements. This kind of
strategy selection is totally stochastic while the task allocation
algorithm follows a logical path. The ideal system is the one that
analyzes the optimal strategic path and consistently follows
strategies that bring maximum outcome. The result regarding the
community that follows the random strategy shows how stochastic
decision making degrades the community budget, but still this
result outperforms the one of the purely competitive community. In
the last case, all the services follow the competitive strategy
and the frequency of getting rejected from a task is relatively
high. In a community with limited number of tasks, the competitive
strategy for all services highly influences the community budget
because a potential group of services are losing at every run.

@@

Figure \ref{membership_fee_graph} depicts how increasing the membership fee which is analogious to getting lower amount of income when doing tasks successfuly affects the overall budget of webservices using different decision making processes. In Figure \ref{membership_fee_graph} part(a) we set the membership fee to 2, in \ref{membership_fee_graph} part(b) to reletively high value of 5 and \ref{membership_fee_graph} part(a) shows the result when the membership fee is set to very high fee of 10.
